TBD

### 2020-11-03 outputs/paper/paper.Rmd
9.22

```{r}
# Setup data for the pie chart and mutate a variable that details proportions for various responses. 
incomeinfo <- tbdata %>% group_by(household_income_grouped) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
# Graph the pie chart using ggplot; Set colour scheme, font, etc. 
incomegraph <- incomeinfo %>% ggplot(aes(x = "", y = prop, fill = household_income_grouped)) + 
      geom_bar(width = 1, stat = "identity") + 
      coord_polar("y", start = 0) +
      scale_fill_brewer(palette = "Accent") +
      theme_void() +
      ylab("") + xlab("") + 
     labs(title = "", fill="Household Income") +
     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=0, size = 4.7) +
     theme(text = element_text(size=13))
incomegraph
```

```{r}
# Setup data for the pie chart and mutate a variable that details proportions for various responses. 
raceinfo <- tbdata %>% group_by(race_ethnicity) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
# Graph the pie chart using ggplot; Set colour scheme, font, etc. 
racegraph <- raceinfo %>% ggplot(aes(x = "", y = prop, fill = race_ethnicity)) + 
      geom_bar(width = 1, stat = "identity") + 
      coord_polar("y", start = 0) +
      scale_fill_brewer(palette = "Set3") +
      theme_void() +
      ylab("") + xlab("") + 
     labs(title = "", fill="What is your race?") +
     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=0, size = 3) +
     theme(text = element_text(size=13))
racegraph
```

@@

```{r}
# Setup data for the pie chart and mutate a variable that details proportions for various responses. 
ageinfo <- tbdata %>% group_by(age_group) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
# Graph the pie chart using ggplot; Set colour scheme, font, etc. 
agegraph <- ageinfo %>% ggplot(aes(x = "", y = prop, fill = age_group)) + 
      geom_bar(width = 1, stat = "identity") + 
      coord_polar("y", start = 0) +
      scale_fill_brewer(palette = "Set3") +
      theme_void() +
      ylab("") + xlab("") + 
     labs(title = "", fill="Age Groups") +
     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=0, size = 4)+
     theme(text = element_text(size=13))
agegraph
```

>>>>

In Figure [] below, we can see that the distribution is largely skewed towards families with income less than $50,000:
```{r}
# Setup data for the pie chart and mutate a variable that details proportions for various responses. 
incomeinfo <- tbdata %>% group_by(household_income_grouped) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
# Graph the pie chart using ggplot; Set colour scheme, font, etc. 
incomegraph <- incomeinfo %>% ggplot(aes(x = "", y = prop, fill = household_income_grouped)) + 
      geom_bar(width = 1, stat = "identity") + 
      coord_polar("y", start = 0) +
      scale_fill_brewer(palette = "Accent") +
      theme_void() +
      ylab("") + xlab("") + 
     labs(title = "", fill="Household Income") +
     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=0, size = 4.7) +
     theme(text = element_text(size=13))
incomegraph
```
Because of the skewed distribution of income, we can justify using post stratification. Clearly, those with income less than $50,000 are overrepresented in the dataset as they take up 50% of the responses, therefore it is appropriate to use post stratification.

We can see a similar skewed distribution in Figure [] below: 
```{r}
# Setup data for the pie chart and mutate a variable that details proportions for various responses. 
raceinfo <- tbdata %>% group_by(race_ethnicity) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
# Graph the pie chart using ggplot; Set colour scheme, font, etc. 
racegraph <- raceinfo %>% ggplot(aes(x = "", y = prop, fill = race_ethnicity)) + 
      geom_bar(width = 1, stat = "identity") + 
      coord_polar("y", start = 0) +
      scale_fill_brewer(palette = "Set3") +
      theme_void() +
      ylab("") + xlab("") + 
     labs(title = "", fill="What is your race?") +
     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=0, size = 3) +
     theme(text = element_text(size=13))
racegraph
```
Looking at the distribution of race, we can see that 75% of the respondants from the survey are white. Since the distribution does not represent minorities, we can justify using post stratification.

@@

Lastly, in Figure [] below, we can see how the population aged older than 76 are barely represented: 
```{r}
# Setup data for the pie chart and mutate a variable that details proportions for various responses. 
ageinfo <- tbdata %>% group_by(age_group) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
# Graph the pie chart using ggplot; Set colour scheme, font, etc. 
agegraph <- ageinfo %>% ggplot(aes(x = "", y = prop, fill = age_group)) + 
      geom_bar(width = 1, stat = "identity") + 
      coord_polar("y", start = 0) +
      scale_fill_brewer(palette = "Set3") +
      theme_void() +
      ylab("") + xlab("") + 
     labs(title = "", fill="Age Groups") +
     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=0, size = 4)+
     theme(text = element_text(size=13))
agegraph
```
The fact that those age 76+ make up only a 3% of the data could be a product of the fact that the survey was completed online. Clearly, the survey doesn't accurately represent those aged older than 76 posing the question — does our data represent the United States? The answer is no. To adjust for the fact that the population aged 76+, we will use post stratification.
